\documentclass[a4paper,margin,line]{resume}
\usepackage[defblank]{paralist}
\usepackage{pdfpages}
\usepackage{anysize}
\usepackage[unicode]{hyperref}
\hypersetup{
	pdftitle={Susan Lunn's Resume},
	pdfauthor={Susan Lunn},
	pdfborder={0 0 0},
	unicode=true
}
\marginsize{0.375in}{1.875in}{0.375in}{0.375in}
\setdefaultitem{\footnotesize \textbullet}{}{}{}{}{}
\setdefaultleftmargin{0em}{}{}{}{}{}
\setdefaultenum{$\bullet$}{(1)}{}{}{}{}
\newcommand{\rurl}[1]{\hfill {\footnotesize \url{#1}}}
\newcommand{\rdate}[1]{\hfill {\small #1}}
\renewcommand{\employer}[5]{\item[#1] - #2 \rdate{#3} \\* #4 \rurl{#5} \\*}
\begin{document}
\name{\Large Susan K. Lunn}
\begin{resume}
\section{\mysidestyle Contact \\ Information} \vspace{2mm}
	\begin{asparablank}
		\item Rochester Institute of Technology \hfill (802)-309-4493
		\item PO Box 92423 \hfill slunn@csh.rit.edu
		\item Rochester, NY 14692 \hfill github.com/emollient
	\end{asparablank}

\section{\mysidestyle Objective}
	\begin{asparablank}
    	\item Seeking 6 month co-op employment starting May 2015 until December
        2015.
	\end{asparablank}

\section{\mysidestyle Education}
	\begin{compactdesc}
		\item[Rochester Institute of Technology] - Rochester, NY \rdate{August 2013 - Present}
		\begin{compactitem} { \small
			\item Major: B.S./M.S. Computer Science
		} \end{compactitem}
		\begin{compactitem} { \small
			\item Expected Graduation: May 2018
		} \end{compactitem}
	\end{compactdesc}

\section{\mysidestyle Technical Skills \& Certifications}
	\begin{compactdesc}
		\item[Languages: ] \begin{inparaenum} { \small
			\item Python
            \item C
			\item Bash
			\item Java
		} \end{inparaenum}
        \item[Exposed Languages: ] \begin{inparaenum}{ \small
            \item Julia
            \item Haskell
            \item Go
            \item Javascript
        } \end{inparaenum}
		\item[Operating Systems: ] \begin{inparaenum} { \small
            \item Linux 
			\item Mac OS X
		} \end{inparaenum}
		\item[Tools: ] \begin{inparaenum} { \small
            \item Git
			\item Make
			\item \LaTeX
		} \end{inparaenum}
	\end{compactdesc}

\section{\mysidestyle Current Personal Projects}
    \begin{asparadesc}
       \employer{Deploying Docker}{November 2014}{}{}{}
       \small
       Deployed a linux container platform that allows the automation of
       software applications on a local Computer Science House machine known
       as Hactar. Docker builds on top of a few different linux container 
       technologies, and we used it as a test platform for in-house written 
       applications. 
       \normalsize
       \\
       \employer{Algorithmically}{November 2014}{}{}{}
       \small 
       Implements several different common algorithms and data structures in 
       popular as well as new, cutting edge programming languages. Then running
       the unix time command and some nifty bash, it records the time each
       algorithm takes to run and stores the value. The values are then
       graphified and published online, using D3 javascript to graphify them.
       \normalsize
       \\
       \employer{MyShell}{December 2014}{}{}{}
       \small
       Wrote a basic unix shell in C that implements piping, standard I/O
       redirection and all commands found within the PATH variable as 
       well as a set of its own internal commands.
       \normalsize
       \\
        \employer{Git by a Truck}{September 2014}{}{}{https://github.com/ryansb/gitbyatruck}
        \\
       \small
       It is a replacement for the tool known as "git by a bus" which scans
       through a repository and checks which developers commited to which file.
       "Git by a Truck" answers the question about a repository "if 20\% of the
       developer team were to be hit by a bus, would the project survive?" The
       project is written using the Pyramid framework, a python web framework. 
       Using libgit for C bindings, and stored procedures that are triggered 
       on insert, we add information about a repository and process it. The
       front-end rest points are currently being written by me, as well as pretty D3
       javascript graphs.
       \normalsize
    \end{asparadesc}

\section{\mysidestyle Experience}
	\begin{asparadesc}
        \employer{Earth Moves}{April 2014 to August 2014}{}{Web Developer}{}
        \\
		\small
        Worked on several applications per client request. My two main projects
        were building a web scraper to pull thousands of eye glass frames and
        aggregate them, from several websites, this was written using the Python
        library Scrapy and bootstrap CSS to display data. Then I built a web
        application for doctor's and hospitals to manage their operation trays,
        which was written in Python using the Pyramid Pylons framework and
        bootstrap CSS framework. \normalsize
		\\
		\employer{Magic@Rochester Institute of Technology}{August 2014 to Present}{}{Java Back-end Web Developer}{http://magic.rit.edu/main/index.html}
        \\
		\small
        Working on writing a web application that uses ArchivesSpace - a
        standard for museum websites, to display data about toy makers. It is
        meant to be displayed in a children's museum soon. \end{asparadesc}
\section{\mysidestyle Extracurricular Clubs \& Activities}
	\begin{asparablank}
        \item FOSSBox({\small Free Open Source Software Box}) - Active member\rurl{http://magic.rit.edu/foss/}
		\item CSH ({\small Computer Science House}) - Full Active member\rurl{http://www.csh.rit.edu/}
		\item US FIRST Robotics Team 3397 - {\small Lead programmer}\rurl{http://www.usfirst.org/}
	\end{asparablank}

\end{resume}
\end{document}

% vim:set ai
